Reach OPT MSNA 2021

### 2021-06-28 MSNA_2021_Monitoring_report.Rmd
data cleaning update
Data cleaning update
Time limit changes

assessment_start_date <- as.Date("2021-06-16")

@@

time_limit <- 15
flag_time_limit <- 30
max_interv <- 10

@@

############ add full strata
######NOTE ::: CHANGE THE OSLO AREA TO REFLECT THE TOOL, A, B, C
df <- df %>%
  mutate(across(everything(), as.character)) %>%
  mutate(strata =
           case_when(location == "west_bank" & (oslo_area == "area_a" | oslo_area == "area_b") ~ "Area_AB",
                     location == "west_bank" & oslo_area == "area_c" ~ paste(hh_location_wb, oslo_area, sep = "_"),
                     location == "gaza" ~ hh_location_gaza,
                     location == "ej"~ "East_Jerusalem",
                     TRUE  ~  'H2'))

@@

enumerator_productivity_final <- rbind(enumerator_productivity_many, enumerator_productivity_less)%>% 
  arrange(desc(Date) )

@@

# Enumerator with short interv duration
short_interviews_by_enum <- df %>% 
  filter(df$consent == "yes" ) %>% 
  dplyr::filter(interview_duration < time_limit & today > "2021-06-16") %>%

@@

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(survey_status_per_day)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```
<center>**Interview Method - Completed Interviews**</center> </br>

>>>>

assessment_start_date <- as.Date("2021-06-15")

@@

time_limit <- 10
flag_time_limit <- 20
max_interv <- 10

@@

############ add full strata
######NOTE ::: CHANGE THE OSLO AREA TO REFLECT THE TOOL, A, B, C
df <- df %>%
  mutate(across(everything(), as.character)) %>%
  mutate(strata =
           case_when(location == "west_bank" & (oslo_area == "A" | oslo_area == "B") ~ "Area_AB",
                     location == "west_bank" & oslo_area == "C" ~ paste(hh_location_wb, oslo_area, sep = "_"),
                     location == "gaza" ~ hh_location_gaza,
                     location == "ej"~ "East_Jerusalem",
                     TRUE  ~  'H2'))

@@

enumerator_productivity_final <- rbind(enumerator_productivity_many, enumerator_productivity_less)%>% 
  dplyr::select(Enumerator, Interviews) %>% 
  arrange(desc(Enumerator))

@@

# Enumerator with short interv duration
short_interviews_by_enum <- df %>% 
  filter(df$consent == "yes" ) %>% 
  dplyr::filter(interview_duration < time_limit & today > "2021-06-15") %>%

@@

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(survey_status_per_day)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```
<center>**Completed Interviews**</center> </br>
